Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2020-10-03 manuscript/manuscript.Rmd
Minor typos

We use a conjoint experiment to study the simultaneous effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization. Conjoint analysis allows us to elicit donor preferences without respondents explicitly stating their exact preferences. This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@Helfer:206; @Mummolo:2016; @KnudsenJohannesson:2019]. Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy.

@@

More importantly, we find that trust in political institutions and in charitable organizations matters substantially in shaping donor preferences. Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments. Personas with low social trust tend to be wary of negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations. This could imply who donors that are the most trusting and involved could remain supportive when charities face government criticism and crackdown. The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.

>>>>

We use a conjoint experiment to study the simultaneous effects of organizational characteristics and individual attributes on individuals' preferences to donate to a nonprofit organization. Conjoint analysis allows us to elicit donor preferences without respondents explicitly stating their exact preferences. This kind of analysis is commonly used in marketing to reveal consumer preferences for hypothetical products, and has become increasingly popular in political science and public policy [@Helfer:2016; @Mummolo:2016; @KnudsenJohannesson:2019]. Because we are interested in exploring the complexity behind the decision to donate, we apply conjoint methods to the study of nonprofits and philanthropy.

@@

More importantly, we find that trust in political institutions and in charitable organizations matters substantially in shaping donor preferences. Personas with high levels of social and charitable trust prefer donating to human rights organizations that have friendly relationships with their host governments, while personas with low trust are drawn more to emergency response and refugee relief organizations with unfriendly relationships with their host governments. Personas with low social trust tend to be wary of negative host-country relationships and strongly prefer to donate to organizations that are friendly with their host governments, while personas with high social trust are more willing to stick with legally besieged organizations. This could imply who donors who are the most trusting and involved could remain supportive when charities face government criticism and crackdown. The global crackdown on NGOs may also possibly sour NGOs' least trusting individual donors.
